---
title: "ConfidenceIntervals"
author: "Anna Jones"
date: "15/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Confidence Intervals

### Intro

Looking at the book

Statistical Inference via Data Science
A moderndive into R and the tidyverse

https://moderndive.com/9-confidence-intervals.html#needed-packages-6

Chapter 9: Confidence Intervals

***

### Libraries

```{r libraries}
library(dplyr)
library(ggplot2)
library(janitor)
library(moderndive)
library(infer)
```

The moderndive package contains a sample of 40 pennies collected and minted in the United States. Let’s explore this sample data first:

```{r}
pennies_sample
```

### Exploratory Analysis

First, let’s visualize the values in this sample as a histogram:

```{r}
ggplot(pennies_sample, aes(x = age_in_2011)) +
  geom_histogram(bins = 10, color = "white")
```

We see a roughly symmetric distribution here that has quite a few values near 20 years in age with only a few larger than 40 years or smaller than 5 years. If pennies_sample is a representative sample from the population, we’d expect the age of all US pennies collected in 2011 to have a similar shape, a similar spread, and similar measures of central tendency like the mean.

```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

